---
title: "CTO Exploratory Data Analysis"
author: "Uche Ezema"
date: "2023-02-28"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries and data, include=FALSE}
library(tidyverse)

cto <- read_csv("CTO.csv")

```

## CTO Logistics Data

This is an exploratory data analysis of the CTO Logistics Questionnaire. Only a descriptive analysis of charts and tables are covered to provide insight for further inferential analysis. The report has been built with **R Markdown.** 


### 1.1 Logistics Supply Chain System (LSCS) components that facilities have.
```{r components, echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
lscs <- cto %>% 
  select(product_selection_register:policy_document) %>% 
  pivot_longer(cols = c(product_selection_register:policy_document)) %>% 
  filter(!is.na(value)) %>% 
  group_by(name) %>% 
  summarise(Freq = sum(value)) %>% 
  ggplot(aes(x = reorder(name, Freq), y = Freq))+
  geom_col(stat = "identity")+
  coord_flip()+
  labs(title = "Distribution of LSCS components available in facilities",
       x = "Frequency",
       y = "LSCS component")
lscs
```


### 1.2 Training status of respondents

Respondents that have ever received logistics training:

```{r training, echo=FALSE, fig.width=8}
lscs <- cto %>% 
  ggplot(aes(x = logi_training))+
  geom_bar(stat = "count")+
  labs(title = "Respondents that ever received logistics training",
       x = "Training status",
       y = "Frequency")
lscs
```


### 1.3 Different methods used by health facility respondents for selecting commodities:

```{r methods, echo=FALSE, fig.width=8}
lscs <- cto %>% 
  ggplot(aes(x = commodity_selection_method))+
  geom_bar(stat = "count")+
  labs(title = "Methods of commodities selection used in the facilities",
       x = "Methods of commodity selection",
       y = "Frequency")
lscs
```


### 1.4 Respondents opinion about what effective logistics system can achieve:

```{r effective, echo=FALSE, fig.width=8}
lscs <- cto %>% 
  ggplot(aes(x = what_effective_log_sys_can_achieve))+
  geom_bar(stat = "count")+
  labs(title = "What can effective logistics system achieve?",
       x = "Opinion",
       y = "Frequency")
lscs
```

### 1.5 Including Plots

Respondents that have ever received logistics training:

```{r pressure1, echo=FALSE, fig.width=8}
lscs <- cto %>% 
  ggplot(aes(x = logi_training))+
  geom_bar(stat = "count")+
  labs(title = "Respondents that ever received logistics training",
       x = "Training status",
       y = "Frequency")
lscs
```

## 1.6 Including Plots

Respondents that have ever received logistics training:

```{r pressure2, echo=FALSE, fig.width=8}
lscs <- cto %>% 
  ggplot(aes(x = logi_training))+
  geom_bar(stat = "count")+
  labs(title = "Respondents that ever received logistics training",
       x = "Training status",
       y = "Frequency")
lscs
```

## 1.7 Including Plots

Respondents that have ever received logistics training:

```{r pressure3, echo=FALSE, fig.width=8}
lscs <- cto %>% 
  ggplot(aes(x = logi_training))+
  geom_bar(stat = "count")+
  labs(title = "Respondents that ever received logistics training",
       x = "Training status",
       y = "Frequency")
lscs
```

## 1.8 Including Plots

Respondents that have ever received logistics training:

```{r pressure4, echo=FALSE, fig.width=8}
lscs <- cto %>% 
  ggplot(aes(x = logi_training))+
  geom_bar(stat = "count")+
  labs(title = "Respondents that ever received logistics training",
       x = "Training status",
       y = "Frequency")
lscs
```

## 1.9 Including Plots

Respondents that have ever received logistics training:

```{r pressure5, echo=FALSE, fig.width=8}
lscs <- cto %>% 
  ggplot(aes(x = logi_training))+
  geom_bar(stat = "count")+
  labs(title = "Respondents that ever received logistics training",
       x = "Training status",
       y = "Frequency")
lscs
```

## 1.10 Including Plots

Respondents that have ever received logistics training:

```{r pressure6, echo=FALSE, fig.width=8}
lscs <- cto %>% 
  ggplot(aes(x = logi_training))+
  geom_bar(stat = "count")+
  labs(title = "Respondents that ever received logistics training",
       x = "Training status",
       y = "Frequency")
lscs
```
